\chapter{Introduction}\label{C:intro}
The investigation of droplet impact and evaporation is an area of experimentation of interest and application to various industry. Such as milk powder spray drying, ink jet printing, and applications of evaporative cooling. This project will continue on from a previous instrumentation setup, evaluate its shortcomings, and design the next generation to improve the reliability and usability of the collected data and introduce methods of automating the process. 

Report covers the key problem the experimental setup that the project aims to improve, and what are the main factors that can introduce variation into the results. An overview and evaluation of the current/previous system and the variability of its results and possible sources of that inconsistency. It was briefly cover other similar systems in literature can what they control/how. Then it will redefine the project scope, its objectives and what variables its aim to control and how. Finally it will cover what work has been down and where the current progress and results stand as well as detailing difficulties/decisions made along then way.  

\section*{The Experiment}

A droplet of liquid (concentrated milk, water, etc) is deposited on a heated substrate (stainless steel, copper, glass). The temperature of the substrate in monitored, along with the progression of the droplets impact and evaporation being captured with 2 cameras; above and profile. This produces a multidimensional perception of the developing behaviour and characteristics of the droplet over time. This usually take 1-2mins per droplet.

\subsection*{Problems}

Such a process